The Concurrent Calculi Formalisation Benchmark

### 2023-10-17 paper/paper.tex
Typo

This challenge formalises a proof that requires explicit scope extrusion.
Scope extrusion is the notion that a process can send restricted names to another process, as long as the restriction can safely be ``extruded'' (i.e.\ expanded) to include the receiving process.
This e.g.\ allows a process to set up a private connection by sending a restricted name to another process, then using this name for further communication
The key issue of this challenge is reasoning about names that are ``in the process'' of being scope-extruded, which often presents difficulties for the mechanisation of binders.

>>>>

This challenge formalises a proof that requires explicit scope extrusion.
Scope extrusion is the notion that a process can send restricted names to another process, as long as the restriction can safely be ``extruded'' (i.e.\ expanded) to include the receiving process.
This e.g.\ allows a process to set up a private connection by sending a restricted name to another process, then using this name for further communication.
The key issue of this challenge is reasoning about names that are ``in the process'' of being scope-extruded, which often presents difficulties for the mechanisation of binders.
